---
title: "Data Science for Public Health - Configure RStudio to execute Stata commands"
author: "H. Langet, S. Lwambura and C.Festo"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE)
```

# Load the RStata library

`RStata` is a simple R / Stata interface which enable the user to:

* execute Stata commands (both inline and from a .do file) from R;
* pass a data.frame to Stata;
* return a data.frame to R;
* include Stata chunks in knitr documents (however each chunk is independent from the others; feature tested with LaTeX/Linux).

```{r}
library(RStata)
```

# Find your Stata binary path

The function `chooseStataBin` from the `RStata` library allows you to browse and set the path to your Stata binary executable.

```{r}
stata_bin_path <- RStata::chooseStataBin()
print(stata_bin_path)
```

You should normally get a path which is of the format: `"\"C:\\Program Files\\Stata16\\StataIC-64\""` where the .exe extension has been removed from the path.

# Add your Stata binary path to your .Rprofile

The Stata binary path setting we just created will be lost if your RStudio is closed.
To keep this setting each time you are using RStudio, let us add the Stata binary path as an option to `.Rprofile`, which is your user-specific R configuration file.

## Load the usethis library

```{r}
library(usethis)
```

`Usethis` is a workflow package: it automates repetitive tasks that arise during project setup and development, both for R packages and non-package projects.

## Open your user-specific R configuration file

The function `edit_r_profile` from the `usethis` library allows to open your configuration file `.Rprofile`.

```{r}
usethis::edit_r_profile("user")
```
Add the following two lines in the Rprofile file that you have just opened:

* options("RStata.StataPath" = ...)
* options("RStata.StataVersion" = ...)

You need to indicate the path to your Stata binary executable in the `RStata.StataPath` option (e.g., "\"C:\\Program Files\\Stata16\\StataIC-64\"") and the version of your Stata (e.g., 16) in the `RStata.StataVersion` option.

Once you are done, save and close your `.Rprofile`.
