---
title: "Getting started with R markdown to generate reports using R and Stata"
author: "H. Langet, S. Godfrey and C.Festo"
date: "`r Sys.Date()`"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# About RStata

`RStata` is a simple R / Stata interface which enable the user to:

* execute Stata commands (both inline and from a .do file) from R;
* pass a data.frame to Stata;
* return a data.frame to R;
* include Stata chunks in knitr documents (however each chunk is independent from the others; feature tested with LaTeX/Linux).

# Find your Stata binary path

Find and format the path to your Stata binary executable

```{r}
library(RStata)
stata_bin_path <- RStata::chooseStataBin()
print(stata_bin_path)
```

You should normally get a path which is similar to `"\"C:\\Program Files\\Stata16\\StataIC-64\""`

As this configuration is lost when R is closed, let us add the Stata binary path in your `.Rprofile`. 

# Add your Stata binary path to your .Rprofile



## Open configuration file

```{r}
library(usethis)
usethis::edit_r_profile("user")
```
