---
title: "Data Science for Public Health - Use Stata with R Markdown"
author: "H. Langet, S. Lwambura and C.Festo"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

Load all the R libraries that are needed to run this document.

## Load RStata

The `RStata` package is a simple R / Stata interface which enable the user to:

* execute Stata commands (both inline and from a .do file) from R;
* pass a data.frame to Stata;
* return a data.frame to R;
* include Stata chunks in knitr documents (however each chunk is independent from the others; feature tested with LaTeX/Linux).

```{r}
library(RStata)
```

## Load Haven

The `Haven` package enables R to read and write various data formats used by other statistical packages by wrapping the `ReadStat` C library. `Haven` currently supports SAS, SPSS and Stata.

```{r}
library(haven)
```

## Load Psych

```{r}
library(psych)
```

# Execute Stata commands from R

## Execute a command line

The `stata` function from the `RStata` library allows you to execute Stata commands from your R session.

```{r}
RStata::stata('di "This sentence is displayed using Stata"')
```

## Execute an entire .do file

You can execute an entire .do file.

```{r}
RStata::stata("demo_do_file.do")
```

# Use Stata datasets

## Return R data frame objects from Stata commands

You need to set the `data.out` parameter to `TRUE` when using the `stata` function to return an R data frame object that can be used within the R session.

For those who have never used R before, In R we need to store the dataset (also referred to as dataframe) into a variable in order to be able to use the dataset. the `<-` is an assignment operation, `=` can also be used.

In the example below, the automobile dataset shipped with Stata is loaded and the returned data frame is stored in a variable named `df1`. 

```{r}
df1 <- RStata::stata("sysuse auto",
                     data.out = TRUE)
```

You can use the returned data frame in R. For instance, you can generate a simple formatted table to display the content of the returned data frame by using the `kable` function from the `knitr` package.

```{r}
knitr::kable(df1)
```

## Read Stata DTA files

You can load Stata .dta data by using the `read_dta` function from the `haven` package.

```{r}
df2 <- haven::read_dta("iris.dta")
```

```{r}
knitr::kable(df2)
```
# Combine Stata and R

It can be very handy to combine Stata and R, for instance if you want to clean your data in Stata and then plot it in R using ggplot2, or vice-versa.

## Use Stata after R

```{r}
RStata::stata("codebook",
              data.in = df2)
```

## Use R after Stata

```{r}
df3 <- mtcars
psych::describe(df3)
plot(df3$hp, df3$disp, xlim=c(0,500), ylim=c(0,500))
```
Use the `drop` command to remove observations where the the variable `disp` is below 200.

```{r}
df4 <- RStata::stata("drop if disp <= 200",
                     data.in = df3,
                     data.out = TRUE)
```
```{r}
psych::describe(df4)
plot(df4$hp, df4$disp, xlim=c(0,500), ylim=c(0,500))
```

an additional example for using stata from within R is adding new variable in a dataset. Using the df2 data we imported we can add a new variable called **sepalarea** using the stata command. 
Note we have to specify the `data.out` to be able to return the resulting dataset

```{r}
df2 <- RStata::stata("gen sepalarea=sepallength*sepalwidth",
                     data.in=df2,
                     data.out=TRUE)
knitr::kable(df2)
```

# Acknowledgment

This RMarkdown document is inspired by the [post from Ignacio Riveros](https://ignacioriveros1.github.io/r/2020/03/22/r_and_stata.html).
