---
title: "Use Stata and Python in your Quarto document"
subtitle: "Data Science for Public Health - Day 01 - Session 02"
date: "2022-09-26"
format:
  html:
    toc: true
    number-sections: true
editor: visual
engine: knitr
bibliography: references.bib
---

# Introduction

The number of languages and runtimes used for scientific discourse is very broad (and the RStudio and Jupyter ecosystems in particular are extraordinarily popular).

Quarto was developed to be multilingual, beginning with R, Python, Javascript, and Julia, with the idea that it will work even for languages that don't yet exist.

# Use Stata

# For (advanced) Python/R Markdown users only

You still need to import the R package `reticulate` if you want to use the Knitr engine and manipulate Python objects within R code chunks.

```{r}
#| echo: true
library(reticulate)
```

## Manipulation of R objects in Python code chunks

R objects can be manipulated in Python code chunks by referring to them as `r.`

```{r}
#| echo: true
val <- 10
```

```{python}
#| echo: true
val = 5
print(r.val)
```

## Manipulation of Python objects in R code chunks

Python objects can be manipulated in R code chunks by referring to them as `py$`

```{r}
#| echo: true
print(val)
print(py$val)
```

## References
