---
title: ":orange_book: Practical"
warning: false
---

## Introduction

### Overview

This tutorial is adapted from the excellent [Machine learning in Python with scikit-learn](https://www.fun-mooc.fr/en/courses/machine-learning-python-scikit-learn/)

### Learning objectives

## Question

We are interested in predicting **referral in children under 5** based on two of the clinical measurements at the consultation:

-   **age in months** and
-   **param2**.

```{r}
#| echo: fenced
library(tidyverse) # includes dplyr and tibble
library(skimr)
library(ggplot2)
library(DataExplorer)
```

## Load the data

The dataset is stored in **dataset1.dta**.

Read the dataset and store it into a dataframe called **df**.

Let’s first load the entire adult dataset containing both numerical and categorical data.

```{r}
#| echo: fenced
df <- openxlsx::read.xlsx("./data/dataset3.xlsx")
```

## Data exploration

We want to do some data exploration to get an initial understanding of the data. Before building a predictive model, it is always a good idea to look at the data:

-   maybe the task you are trying to achieve can be solved without machine learning;
-   you need to check that the information you need for your task is actually present in the dataset;
-   inspecting the data is a good way to find peculiarities. These can arise during data collection (for example, malfunctioning sensor or missing values), or from the way the data is processed afterwards (for example capped values).

### Variables / features

::: panel-tabset
#### :pencil2: Exercise 1

Examine the structure of the data, including variable names, labels. 

1. How many variables are numerical?
2. How many features are categorical?

::: callout-tip
-   Stata: use the [codebook](https://www.stata.com/manuals/dcodebook.pdf) command
-   R: use the [skim](https://docs.ropensci.org/skimr/reference/skim.html) function from the `skimr` package
:::

Display the variables/features **child_id**, **test** and **test** for the **10 first observations/samples** in the data.

::: callout-tip
-   Stata hint: use the the combination of `describe` and `list` command to inspect the data
-   R hint: you need to load the `dplyr` library to use piping
:::

```{r}
#| echo: fenced
# Write your code here
```

#### R

```{r}
#| echo: fenced
df %>%
  skimr::skim()
```

```{r}
#| echo: fenced
df <- df %>%
  tibble::remove_rownames() %>%
  tibble::column_to_rownames(var="RCT_child_ID") %>% 
  dplyr::mutate(across(c(RCT_CTX_month,
                         RCT_CTX_day_of_week,
                         RCT_SDC_sex, 
                         RCT_CLIN_fever,
                         RCT_CLIN_cough,
                         RCT_CLIN_diarrhoea,
                         RCT_RX_preconsult_antibiotics,
                         RCT_RX_preconsult_antimalarials,
                         RCT_CTX_district,
                         RCT_CTX_area,
                         RCT_CTX_facility_type,
                         RCT_TEST_malaria_done,
                         RCT_TEST_malaria_type,
                         RCT_TEST_malaria_result,
                         RCT_DX_malaria,
                         RCT_DX_malaria_severe,
                         SPA_CLIN_fever_reported,
                         SPA_CLIN_fever_investigated,
                         SPA_CLIN_fever,
                         RCT_DX_severe,
                         RCT_RX_antimalarials,
                         RCT_RX_antimalarial_parenteral,
                         RCT_RX_ACT,
                         RCT_RX_AL,
                         RCT_RX_artemether,
                         RCT_RX_artesunate,
                         RCT_RX_primaquine,
                         RCT_RX_quinine,
                         RCT_RX_antibiotics,
                         RCT_RX_antibiotics_src_text,
                         RCT_MGMT_referral_src_caregiver,
                         RCT_MGMT_referral_src_registry,
                         RCT_CTX_SPA_obs,
                         RCT_CTX_SPA_obs_after_lab,
                         SPA_MEAS_temperature_done,
                         SPA_MGMT_admission,
                         SPA_MGMT_referral_other_facility,
                         SPA_MGMT_referral_other_provider,
                         SPA_TEST_malaria_ordered,
                         SPA_RX_prereferral),
                       factor))
```

```{r}
#| echo: fenced
df %>%
  skimr::skim()
```

:::

Numerical variables can be naturally handled by machine learning algorithms that are typically composed of a sequence of arithmetic instructions such as additions and multiplications.

```{r}
DataExplorer::plot_missing(df,
                           geom_label_args = list(size = 2, label.padding = unit(0.2, "lines")))
```

```{r}
DataExplorer::plot_bar(df %>% 
                         dplyr::select(-RCT_CTX_facility_ID),
                       by = "RCT_CTX_district")
```

### Target classes

::: panel-tabset

### :pencil2: Exercise 1

What are the different antibiotic treatment classes available in the dataset and how many observations/samples of each types are there?

::: callout-tip
-   Python: select the right column and use the `value_counts` method.
:::

```{r}
#| echo: fenced
# Write your code here
```

### R

```{r}
#| echo: fenced
df %>%
  skimr::skim(RCT_CTX_facility_ID)
```

:::

## Variable/feature distribution

Let's look at the distribution of individual features, to get some insights about the data. We can start by plotting histograms, note that this only works for features containing numerical values.

::: panel-tabset

### :pencil2: Exercise 2

Plot histograms for the numerical variables/features

```{r}
#| echo: fenced
# Write your code here
```

### R

```{r}
#| echo: fenced
# Write your code here
```

```{r}
DataExplorer::plot_histogram(df)
```

:::

::: panel-tabset

### :pencil2: Exercise 3

Show variable/feature distribution for each class.

Looking at these distributions, how difficult do you think it will be to classify the sick children using the `param1` and `param2` variables/features?

```{r}
#| echo: fenced
# Write your code here
```

### R

```{r}
#| echo: fenced
# Write your code here
```

```{r}
#dummy <- caret::dummyVars(" ~ .", data=df)
```

```{r}
ggplot2::ggplot(data = df, aes(x = RCT_SDC_age_in_months, fill = RCT_TEST_malaria_done)) +
  geom_histogram(binwidth = 1, alpha = 0.5, position = "identity") +
  theme_minimal()
```
```{r}
ggplot2::ggplot(data = df, aes(x = RCT_CLIN_fever_onset, fill = RCT_TEST_malaria_done)) +
  geom_histogram(binwidth = 1, alpha = 0.5, position = "identity") +
  theme_minimal()
```

```{r}
ggplot2::ggplot(data = df, aes(x = RCT_CLIN_fever_onset, fill = RCT_TEST_malaria_done)) +
  geom_histogram(binwidth = 1, alpha = 0.5, position = "identity") +
  theme_minimal()
```

```{r}
ggplot2::ggplot(data = df, aes(x = RCT_MEAS_temperature, fill = RCT_TEST_malaria_done)) +
  geom_histogram(binwidth = 0.5, alpha = 0.5, position = "identity") +
  theme_minimal()
```

:::

The score of a model will in general depend on the way we make the training / test split. One downside of doing a single split is that it does not give any information about this variability. Another downside, in a setting where the amount of data is small, is that the data available for training and testing will be even smaller after splitting.
