---
title: ":orange_book: Practical"
warning: false
---

## Introduction

### Overview

This tutorial is adapted from the excellent [Machine learning in Python with scikit-learn](https://www.fun-mooc.fr/en/courses/machine-learning-python-scikit-learn/)

### Learning objectives

## Question

We are interested in predicting **referral in children under 5** based on two of the clinical measurements at the consultation:

-   **param1** and
-   **param2**.

## Load the data

The dataset is stored in **dataset1.dta**.

Read the dataset and store it into a dataframe called **df**.

```{r}
#| echo: fenced
# Write your code here
```

```{r}
#| echo: fenced
library(haven)
df <- haven::read_dta("./data/dataset10.dta")
```

## Visual inspection of the data

We want to do some data exploration to get an initial understanding of the data. Before building a predictive model, it is a good idea to look at the data:

-   maybe the task you are trying to achieve can be solved without machine learning;
-   you need to check that the information you need for your task is actually present in the dataset;
-   inspecting the data is a good way to find peculiarities. These can arise during data collection (for example, malfunctioning sensor or missing values), or from the way the data is processed afterwards (for example capped values).

### Observations/Samples

Display the variables/features **child_id**, **test** and **test** for the **10 first observations/samples** in the data.

::: callout-tip
-   Stata hint: use the the combination of `describe` and `list` command to inspect the data
-   R hint: you need to load the `dplyr` library to use piping
:::

```{r}
#| echo: fenced
# Write your code here
```

```{r}
#| echo: fenced
library(dplyr)
df %>%
  head(10) %>% 
  dplyr::select("child_ID") %>%
  knitr::kable()
```

### Variables/Features

::: panel-tabset

### :pencil2: Exercise 1

How many variables/features are numerical in the dataset?

```{r}
#| echo: fenced
# Write your code here
```

How many variables/features are categorical in the dataset?

```{r}
#| echo: fenced
# Write your code here
```

### Python

To be completed

:::

### Target classes

::: panel-tabset

### :pencil2: Exercise 1

What are the different classes available in the dataset and how many observations/samples of each types are there?

::: callout-tip
-   Python: select the right column and use the `value_counts` method.
:::

```{r}
#| echo: fenced
# Write your code here
```

### Python

To be completed

:::

## Variable/feature distribution

Let's look at the distribution of individual features, to get some insights about the data. We can start by plotting histograms, note that this only works for features containing numerical values.

::: panel-tabset

### :pencil2: Exercise 2

Plot histograms for the numerical variables/features

```{r}
#| echo: fenced
# Write your code here
```

### Python

To be completed

:::

::: panel-tabset

### :pencil2: Exercise 3

Show variable/feature distribution for each class.

::: callout-tip
-   Python: use `seaborn.pairplot`
:::

```{r}
#| echo: fenced
# Write your code here
```

### Python

To be completed

:::

Looking at these distributions, how difficult do you think it will be to classify the sick children using the `param1` and `param2` variables/features?
