---
title: ":orange_book: Malaria case study"
warning: false
---

## Introduction

### Overview

These pages will demonstrate use of Quarto with data from Tanzania. This case study uses data that is not standardized, and so reflects a more challenging use case.

### Learning objectives

## Malaria research questions

Research questions in an enumerated list

## Getting started

#### Access the datasets for this walk-through

* Download the dataset (Excel) here

#### Access the version of the Quarto script used in this walk-through
Download the final RMarkdown template used in this walk-through, to follow-along step-by-step uisng GitHub

#### Quarto resources
Review the R Basics page “Reading a RMarkdown Script”, or reference these resources: Rmarkdown introduction and Rmarkdown authoring basics.

### Dataset description

We will be using data and examples from a real consultation data which occurred in Tanzania between **start date** and **end date**.

DISCLAIMER: The Ifakara Health Institute has approved the use of this data for training purposes. Please note, that some data has been adapted in order to best achieve training objectives. No personally indentifiable information have been kept in this dataset.

Information about the consultations of **10,308 children \[1 day - 59 months\]** from **18 facilities** (dispensaries and health centres) in **Kaliua** District, **Sengerema** District and **Tanga** District, Tanzania. Data were collected using *ODK* (ODK Collect, ODK Central) between **start date** and **end date**. Data were made available by IHI and Swiss TPH and the Tools for Integrated Management of Childhood Illness (TIMCI) project. Data are stored in **dataset1.dta**.

### Data collection

Research assistants recorded the following information from different sources:

-   from the caregiver:
    -   sociodemographic information
    -   information on treatment received before consultation
    -   **clinical presentation** (variables starting with the suffix **CLIN**)
    -   laboratory investigations (variables starting with the suffix **TEST**)
    -   diagnosis (variables starting with the suffix **DX**)
    -   prescribed medication (variables starting with the suffix **RX**)
    -   referral advice will be extracted from clinical notes and / or facility registers (variables starting with the suffix **MGMT**).

Research assistants sought clarification from healthcare providers only in cases where these variables were not clear from the records.

### Data preparation

Data cleaning and data de-identification

Personally identifiable information (PII) were removed.

## Familiarise with the dataset

### Import the data

::: panel-tabset

### :pencil2: Exercise 1

Read the dataset and store it into a dataframe called **df**.

::: callout-tip
Refer to previous session (link to add)
:::

```{r}
#| echo: fenced
# Write your code here
```

### R

```{r}
library(haven)
df <- haven::read_dta("./data/dataset10.dta")
```

```{r}
#| knitr: kable
library(dplyr)
df %>%
  head(5) %>%
  dplyr::select(c("child_ID", "CONSULT_district"))
```

:::

## Population characteristics

### Codebook

### Structure of the data

::: panel-tabset

#### :pencil2: Exercise 2

Examine the structure of the data, including variable names, labels.

::: callout-tip
-   Stata: use the **codebook** function
-   R: use the [skim](https://docs.ropensci.org/skimr/reference/skim.html) function from the `skimr` package
:::

```{r}
#| echo: fenced
# Write your code here
```

#### Stata

```{r}
library(RStata)
RStata::stata("codebook",
              data.in = df)
```

#### R

```{r}
library(skimr)
skimr::skim(df)
```

:::

::: panel-tabset

### :pencil2: Exercise 2

Display descriptive statistics for the following population characteristics:

* age
* sex
* symptoms (fever + duration, cough, diarrhoea)
* pre-consultation abx,
* district
* urban / rural
* type of facility

::: callout-tip
-   R: use the [tbl_summary](https://www.danieldsjoberg.com/gtsummary/reference/tbl_summary.html) function from the `gtsummary` package
:::

```{r}
#| echo: fenced
# Write your code here
```

### Stata

### R

```{r}
#| echo: fenced
#| df-print: kable
library(gtsummary)

df %>%
  select(SDC_age_in_month, SDC_sex, CLIN_fever, CLIN_fever_onset, CLIN_diarrhoea, CLIN_cough) %>%
  tbl_summary()
```

::: 

## Healthcare provider actions

::: panel-tabset

### :pencil2: Exercise 2

Display descriptive statistics fpr the following healthcare provider actions:

* Temperature measured
  * Fever measured
* Fever (temp or history)
* Malaria test
* Any severe diagnosis
* Malaria diagnosis
* Malaria treatment
* Referral

::: callout-tip
-   R: use the [tbl_summary](https://www.danieldsjoberg.com/gtsummary/reference/tbl_summary.html) function from the `gtsummary` package
:::

```{r}
#| echo: fenced
# Write your code here
```

### Stata

### R

```{r}
#| echo: fenced
#| df-print: kable
library(gtsummary)

df %>%
  select(SDC_age_in_month, SDC_sex, CLIN_fever, CLIN_fever_onset, CLIN_diarrhoea, CLIN_cough) %>%
  tbl_summary()
```

::: 

## consultations by facility, by district

## Identify missing values

Identify missing values in each variable: missing_plot

```{r}
library(finalfit)
explanatory = c("CONSULT_facility_ID", "CONSULT_district", "CLIN_fever")
dependent = "DX_malaria"

df %>% 
  finalfit::missing_pattern(dependent, explanatory)
```

## Data analysis plan

Which variables from the dataset you plan to use, and what associations between them you will investigate to help answer your research question.