## Import data - R

### Import Excel data

Read the Excel data set **dataset1.xlsx** and store it into a data frame called **df1**.

Use the [read.xlsx](https://www.rdocumentation.org/packages/openxlsx/versions/4.2.5/topics/read.xlsx) function from the `openxlsx` package.

```{r}
library(openxlsx)
df1 <- openxlsx::read.xlsx("dataset1.xlsx")
```

### Import CSV data

Read the CSV data set **dataset1.csv** and store it into a data frame called **df2**.

Use the [read.csv](https://www.rdocumentation.org/packages/utils/versions/3.6.2/topics/read.table) function from the `haven` package.

```{r}
df2 <- read.csv("dataset1.csv")
```

### Import Stata data

Read the Stata data set **dataset1.dta** and store it into a data frame called **df3**.

Use the [read_dta](https://haven.tidyverse.org/reference/read_dta.html) function from the `haven` package. This package supports SAS, STATA and SPSS software.

```{r}
library(haven)
df3 <- haven::read_dta("dataset1.dta")
```

### Additional question

Can you indicate what variable has been modified in **dataset1** between df1 and df2?

::: callout-tip
Use the R function **comparedf**
:::

```{r}
arsenal::comparedf(df1, df2)
```