---
title: ":orange_book: Malaria case study - Report #1"
execute:
  echo: false
  warning: false
from: markdown+emoji
toc: true
number-sections: true
visual: true
---

## Introduction

```{r}
library(openxlsx)
library(dplyr)
library(skimr)
library(gtsummary)
library(finalfit)
library(ggplot2)
library(ggthemes)
library(networkD3) # For alluvial/Sankey diagrams
library(tidyverse)
```

The data set used for this report is stored in **dataset2.dta**.

```{r}
#| df-print: kable

# 1. Import the dataset and store it into a dataframe called **df**. 
df <- openxlsx::read.xlsx("./data/dataset2.xlsx")

df %>%
  # 2. Select columns **child_ID**, **CTX_month**, **CTX_district**, **SDC_age_in_months** for the first **5** rows in data frame `df`.
  head(5) %>%
  dplyr::select(child_ID,
                CTX_month,
                CTX_district,
                SDC_age_in_months) %>%
  # 3. Display in a table
  knitr::kable(align = c('l', 'c', 'c', 'c'),
               caption = "Extract of the database")
```
## Number of consultations by facility

```{r}
df %>%
  dplyr::group_by(CTX_district,
                  CTX_facility_ID) %>%
  count() %>% 
  ggplot2::ggplot(aes(x = CTX_district,
                      y = n)) + 
  ggplot2::geom_bar(position = position_dodge2(preserve = "single"),
                    stat="identity") +
  ggplot2::labs(x = "", y = "No. consultations") +
  ggthemes::theme_hc()
```

## Population characteristics

### Codebook

#### Numerical variables

+-----------------------------+
| Variable                    |
+=============================+
| SDC_age_in_months           |
+-----------------------------+
| CLIN_fever_onset            |
+-----------------------------+

#### Categorical variables

+-----------------------------+---------------+
| Variable                    | Coding        |
+=============================+===============+
| SDC_sex                     | 1: male       |
|                             |               |
|                             | 2: female     |
|                             |               |
|                             | 98: unknown   |
+-----------------------------+---------------+
| CLIN_fever                  | 0: no         |
|                             |               |
|                             | 1: yes        |
|                             |               |
|                             | 98: not sure  |
+-----------------------------+---------------+
| CLIN_cough                  | 0: no         |
|                             |               |
|                             | 1: yes        |
|                             |               |
|                             | 98: not sure  |
+-----------------------------+---------------+
| CLIN_diarrhoea              | 0: no         |
|                             |               |
|                             | 1: yes        |
|                             |               |
|                             | 98: not sure  |
+-----------------------------+---------------+
| RX_preconsult_antibiotics   | 0: no         |
|                             |               |
|                             | 1: yes        |
+-----------------------------+---------------+
| RX_preconsult_antimalarials | 0: no         |
|                             |               |
|                             | 1: yes        |
+-----------------------------+---------------+
| CTX_district                | Kaliua        |
|                             |               |
|                             | Sengerema     |
|                             |               |
|                             | Tanga         |
+-----------------------------+---------------+
| CTX_area                    | urban         |
|                             |               |
|                             | rural         |
+-----------------------------+---------------+
| CTX_facility_type           | dispensary    |
|                             |               |
|                             | health centre |
+-----------------------------+---------------+

### Structure of the data

Add the following two new variables to data frame `df`

+---------------------------+---------------+
| Variable                  | Coding        |
+===========================+===============+
| SDC_age_category          | \<2 months    |
|                           |               |
|                           | 2-11 months   |
|                           |               |
|                           | 12-23 months  |
|                           |               |
|                           | 24-35 months  |
|                           |               |
|                           | 36-47 months  |
|                           |               |
|                           | 48-59 months  |
+---------------------------+---------------+
| CLIN_fever_onset_category | \<2 days      |
|                           |               |
|                           | 2-3 days      |
|                           |               |
|                           | 4-6 days      |
|                           |               |
|                           | ≥ 7 days      |
+---------------------------+---------------+

```{r}
df <- df %>%
  dplyr::mutate(
    SDC_age_category = dplyr::case_when(
      SDC_age_in_months < 2 ~ "<2 months",
      SDC_age_in_months >= 2 & SDC_age_in_months < 12 ~ "02-11 months",
      SDC_age_in_months >= 12 & SDC_age_in_months < 24 ~ "12-23 months",
      SDC_age_in_months >= 24 & SDC_age_in_months < 36 ~ "24-35 months",
      SDC_age_in_months >= 36 & SDC_age_in_months < 48 ~ "36-47 months",
      SDC_age_in_months >= 48 & SDC_age_in_months < 60 ~ "48-59 months",
      TRUE ~ ""
    )
  ) %>% 
  dplyr::mutate(
    CLIN_fever_onset_category = dplyr::case_when(
      CLIN_fever_onset < 2 ~ "<2 days",
      CLIN_fever_onset >= 2 & CLIN_fever_onset < 4 ~ "2-3 days",
      CLIN_fever_onset >= 4 & CLIN_fever_onset < 7 ~ "4-6 days",
      CLIN_fever_onset >= 7 ~ ">= 7 days",
      TRUE ~ ""
    )
  )
```

```{r}
df <- df %>%
  tibble::remove_rownames() %>%
  tibble::column_to_rownames(var="child_ID") %>% 
  dplyr::mutate(across(c(SDC_sex, 
                         CLIN_fever,
                         CLIN_cough,
                         CLIN_diarrhoea,
                         RX_preconsult_antibiotics,
                         RX_preconsult_antimalarials,
                         CTX_district,
                         CTX_area,
                         CTX_facility_type,
                         SDC_age_category,
                         CLIN_fever_onset_category),
                       factor))
```

```{r}
df %>%
  skim(SDC_age_in_months,
       SDC_sex,
       CLIN_fever,
       CLIN_fever_onset,
       CLIN_diarrhoea,
       CLIN_cough,
       RX_preconsult_antibiotics,
       RX_preconsult_antimalarials,
       CTX_district,
       CTX_area,
       CTX_facility_type)
```
### Descriptive statistics

```{r}
df %>%
  dplyr::select(SDC_age_category,
                SDC_sex,
                CLIN_fever,
                CLIN_fever_onset_category,
                CLIN_diarrhoea,
                CLIN_cough,
                RX_preconsult_antibiotics,
                RX_preconsult_antimalarials,
                CTX_district,
                CTX_area,
                CTX_facility_type) %>%
  gtsummary::tbl_summary(missing_text = "(Missing)")
```

### Age pyramid

```{r}
apyramid::age_pyramid(data = df,
                      age_group = "SDC_age_category",
                      split_by = "SDC_sex",
                      na.rm = TRUE)
```

### Clincial presentation

```{r}
apyramid::age_pyramid(data = df,
                      age_group = "SDC_age_category",
                      split_by = "CLIN_fever",
                      na.rm = TRUE)
```

```{r}
apyramid::age_pyramid(data = df,
                      age_group = "SDC_age_category",
                      split_by = "CLIN_cough",
                      na.rm = TRUE)
```

```{r}
apyramid::age_pyramid(data = df,
                      age_group = "SDC_age_category",
                      split_by = "CLIN_diarrhoea",
                      na.rm = TRUE)
```

## Clinical management

### Codebook

#### Numeric variables

+-----------------------------+
| Variable                    | 
+=============================+
| MEAS_temperature            |
+-----------------------------+

#### Categorical variables

+-----------------------------+------------------------+
| Variable                    | Coding                 |
+=============================+========================+
|                             |                        |
+-----------------------------+------------------------+
| TEST_malaria_result         | 0: negative\           |
|                             | 1: positive\           |
|                             | 2: indeterminate\      |
|                             | 95: unreadable result\ |
|                             | 98: not sure           |
+-----------------------------+------------------------+
| DX_malaria                  | 0: no\                 |
|                             | 1: yes                 |
+-----------------------------+------------------------+
| DX_malaria_severe           | 0: no\                 |
|                             | 1: yes                 |
+-----------------------------+------------------------+
| RX_antimalarials            | 0: no\                 |
|                             | 1: yes                 |
+-----------------------------+------------------------+
| RX_artemether               | 0: no\                 |
|                             | 1: yes                 |
+-----------------------------+------------------------+
| RX_antibiotics              | 0: no\                 |
|                             | 1: yes                 |
+-----------------------------+------------------------+
| MGMT_referral_src_caregiver |                        |
+-----------------------------+------------------------+
| MGMT_referral_src_registry  |                        |
+-----------------------------+------------------------+

### Structure of the data

```{r}
df <- df %>%
  dplyr::mutate(across(c(TEST_malaria_done,
                         TEST_malaria_type,
                         TEST_malaria_result,
                         DX_severe,
                         DX_malaria,
                         DX_malaria_severe,
                         RX_antimalarials,
                         RX_antimalarial_parenteral,
                         RX_artemether,
                         RX_antibiotics,
                         MGMT_referral_src_caregiver,
                         MGMT_referral_src_registry),
                       factor))
```

```{r}
df %>%
  skimr::skim(MEAS_temperature,
              TEST_malaria_done,
              TEST_malaria_type,
              TEST_malaria_result,
              DX_severe,
              DX_malaria,
              DX_malaria_severe,
              RX_antimalarials,
              RX_antimalarial_parenteral,
              RX_artemether,
              RX_antibiotics,
              MGMT_referral_src_caregiver,
              MGMT_referral_src_registry)
```
### Descriptive statistics

```{r}
df <- df %>%
  dplyr::mutate(CALC_temperature_measured = 1 * (!is.na(MEAS_temperature))) %>%
  dplyr::mutate(CALC_fever_measured = 1 * (MEAS_temperature >= 37.5)) %>%
  dplyr::mutate(CALC_fever_all = 1 * ((CLIN_fever == 1) | (!is.na(CALC_fever_measured) & (CALC_fever_measured == 1)))) %>% 
  dplyr::mutate(across(c(CALC_temperature_measured,
                         CALC_fever_measured,
                         CALC_fever_all),
                       factor))
```

```{r}
df %>%
  dplyr::select(CALC_temperature_measured,
                CALC_fever_measured,
                CALC_fever_all,
                TEST_malaria_done,
                TEST_malaria_type,
                TEST_malaria_result,
                DX_severe,
                DX_malaria,
                DX_malaria_severe,
                RX_antimalarials,
                RX_antimalarial_parenteral,
                RX_antibiotics,
                MGMT_referral_src_caregiver,
                MGMT_referral_src_registry) %>%
  gtsummary::tbl_summary(missing_text = "(Missing)")
```
## Fever assessment

```{r}
#| label: fig-temperature-range
#| fig.height: 8
#| fig-cap: "Range of temperature measurements for children with fever (1), without fever (2) and with unkwnown fever presentation (98) by facility"
df %>%
  ggplot2::ggplot(aes(x = CTX_facility_ID,
                      y = MEAS_temperature,
                      fill = CLIN_fever)) +
  ggplot2::ylim(34, 43) + 
  ggplot2::geom_boxplot() + 
  labs(y = "Temperature (in °C)", x = "Facility") +
  coord_flip()
```
```{r}
#| label: fig-fever-prevalence
#| fig.height: 5
#| fig.width: 7
#| fig-cap: "Prevalence of fever when of whole clinic vs of those who measure to indicate bias"
DataExplorer::plot_bar(df %>% 
                         dplyr::select(CALC_fever_all, CALC_temperature_measured),
                       by = "CALC_fever_all")
```
## From fever assessment to malaria treatment

```{r}
df <- df %>%
  dplyr::mutate(CALC_temperature_measured_char = ifelse(!is.na(MEAS_temperature), "Temperature recorded", "Temperature not recorded")) %>%
  dplyr::mutate(CALC_fever_char = ifelse(MEAS_temperature >= 37.5, "Temperature >= 37.5°C", "Temperature < 37.5°C")) %>%
  dplyr::mutate(CLIN_fever_char = ifelse(CLIN_fever == 1, "History of fever", "No history of fever")) %>% 
  dplyr::mutate(TEST_malaria_done_char = ifelse(TEST_malaria_done == 1, "Malaria test recorded", "Malaria test not recorded")) %>% 
  dplyr::mutate(
    TEST_malaria_result_char = dplyr::case_when(
      TEST_malaria_result == 0 ~ "Malaria result negative",
      TEST_malaria_result == 1 ~ "Malaria result positive",
      TEST_malaria_result == 2 ~ "Malaria result indeterminate",
      TEST_malaria_result == 95 ~ "Malaria result unreadable",
      TEST_malaria_result == 98 ~ "Malaria result unknown",
      TRUE ~ ""
    )
  ) %>%
  dplyr::mutate(DX_malaria_char = ifelse(DX_malaria == 1, "Malaria diagnosis", "No malaria diagnosis")) %>% 
  dplyr::mutate(RX_antimalarials_char = ifelse(RX_antimalarials == 1, "Malaria treatment", "No malaria treatment"))
```

::: column-page
```{r}
link_CLIN_fever_and_MEAS_temperature <- df %>%
  select(CLIN_fever_char, CALC_temperature_measured_char) %>%
  count(CLIN_fever_char, CALC_temperature_measured_char) %>%
  rename(source = CLIN_fever_char,
         target = CALC_temperature_measured_char)

fever_measured_links <- df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>% 
  select(CALC_temperature_measured_char, CALC_fever_char) %>%
  count(CALC_temperature_measured_char, CALC_fever_char) %>% 
  rename(source = CALC_temperature_measured_char,
         target = CALC_fever_char)

malaria_test_links <- df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>%
  select(CALC_fever_char, TEST_malaria_done_char) %>%
  count(CALC_fever_char, TEST_malaria_done_char) %>%
  rename(source = CALC_fever_char,
         target = TEST_malaria_done_char)

malaria_test_links2 <- df %>%
  dplyr::filter(CALC_temperature_measured == 0) %>%
  select(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  count(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  rename(source = CALC_temperature_measured_char,
         target = TEST_malaria_done_char)

malaria_results_links <- df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  count(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  rename(source = TEST_malaria_done_char,
         target = TEST_malaria_result_char)

malaria_diagnosis_links <- df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_result_char, DX_malaria_char) %>%
  count(TEST_malaria_result_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_result_char,
         target = DX_malaria_char)

malaria_diagnosis_links2 <- df %>%
  dplyr::filter(TEST_malaria_done == 0) %>% 
  select(TEST_malaria_done_char, DX_malaria_char) %>%
  count(TEST_malaria_done_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_done_char,
         target = DX_malaria_char)

antimalarials_links <- df %>%
  select(DX_malaria_char, RX_antimalarials_char) %>%
  count(DX_malaria_char, RX_antimalarials_char) %>%
  rename(source = DX_malaria_char,
         target = RX_antimalarials_char)

# combine links
links <- bind_rows(link_CLIN_fever_and_MEAS_temperature,
                   fever_measured_links,
                   malaria_test_links,
                   malaria_test_links2,
                   malaria_results_links,
                   malaria_diagnosis_links,
                   malaria_diagnosis_links2,
                   antimalarials_links)

# The unique node names
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
  )

# match to numbers, not names
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

p <- sankeyNetwork(
  Links = links,
  Nodes = nodes,
  Source = "IDsource",
  Target = "IDtarget",
  Value = "n",
  NodeID = "name",
  units = "children",
  fontSize = 12,
  nodeWidth = 30,
  iterations = 0,
  sinksRight = FALSE)        # ensure node order is as in data
p

#links$group <- as.factor(c("type_a","type_a","type_a","type_b","type_b","type_b"))
 
# Add a 'group' column to each node. Here I decide to put all of them in the same group to make them grey
#nodes$group <- as.factor(c("my_unique_group"))
 
# Give a color for each group:
#my_color <- 'd3.scaleOrdinal() .domain(["type_a", "type_b", "my_unique_group"]) .range(["#69b3a2", "steelblue", "grey"])'
```
:::

::: column-page
```{r}
facility1_df <- df %>%
  dplyr::filter(CTX_facility_ID == "F8793")

link_CLIN_fever_and_MEAS_temperature <- facility1_df %>%
  select(CLIN_fever_char, CALC_temperature_measured_char) %>%
  count(CLIN_fever_char, CALC_temperature_measured_char) %>%
  rename(source = CLIN_fever_char,
         target = CALC_temperature_measured_char)

fever_measured_links <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>% 
  select(CALC_temperature_measured_char, CALC_fever_char) %>%
  count(CALC_temperature_measured_char, CALC_fever_char) %>% 
  rename(source = CALC_temperature_measured_char,
         target = CALC_fever_char)

malaria_test_links <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>%
  select(CALC_fever_char, TEST_malaria_done_char) %>%
  count(CALC_fever_char, TEST_malaria_done_char) %>%
  rename(source = CALC_fever_char,
         target = TEST_malaria_done_char)

malaria_test_links2 <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 0) %>%
  select(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  count(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  rename(source = CALC_temperature_measured_char,
         target = TEST_malaria_done_char)

malaria_results_links <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  count(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  rename(source = TEST_malaria_done_char,
         target = TEST_malaria_result_char)

malaria_diagnosis_links <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_result_char, DX_malaria_char) %>%
  count(TEST_malaria_result_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_result_char,
         target = DX_malaria_char)

malaria_diagnosis_links2 <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 0) %>% 
  select(TEST_malaria_done_char, DX_malaria_char) %>%
  count(TEST_malaria_done_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_done_char,
         target = DX_malaria_char)

antimalarials_links <- facility1_df %>%
  select(DX_malaria_char, RX_antimalarials_char) %>%
  count(DX_malaria_char, RX_antimalarials_char) %>%
  rename(source = DX_malaria_char,
         target = RX_antimalarials_char)

# combine links
links <- bind_rows(link_CLIN_fever_and_MEAS_temperature,
                   fever_measured_links,
                   malaria_test_links,
                   malaria_test_links2,
                   malaria_results_links,
                   malaria_diagnosis_links,
                   malaria_diagnosis_links2,
                   antimalarials_links)

# The unique node names
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
  )

# match to numbers, not names
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

p <- sankeyNetwork(
  Links = links,
  Nodes = nodes,
  Source = "IDsource",
  Target = "IDtarget",
  Value = "n",
  NodeID = "name",
  units = "children",
  fontSize = 12,
  nodeWidth = 30,
  iterations = 0,
  sinksRight = FALSE)        # ensure node order is as in data
p
```
:::

::: column-page
```{r}
facility1_df <- df %>% dplyr::filter(CTX_facility_ID == "F7729")

link_CLIN_fever_and_MEAS_temperature <- facility1_df %>%
  select(CLIN_fever_char, CALC_temperature_measured_char) %>%
  count(CLIN_fever_char, CALC_temperature_measured_char) %>%
  rename(source = CLIN_fever_char,
         target = CALC_temperature_measured_char)

fever_measured_links <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>% 
  select(CALC_temperature_measured_char, CALC_fever_char) %>%
  count(CALC_temperature_measured_char, CALC_fever_char) %>% 
  rename(source = CALC_temperature_measured_char,
         target = CALC_fever_char)

malaria_test_links <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>%
  select(CALC_fever_char, TEST_malaria_done_char) %>%
  count(CALC_fever_char, TEST_malaria_done_char) %>%
  rename(source = CALC_fever_char,
         target = TEST_malaria_done_char)

malaria_test_links2 <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 0) %>%
  select(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  count(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  rename(source = CALC_temperature_measured_char,
         target = TEST_malaria_done_char)

malaria_results_links <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  count(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  rename(source = TEST_malaria_done_char,
         target = TEST_malaria_result_char)

malaria_diagnosis_links <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_result_char, DX_malaria_char) %>%
  count(TEST_malaria_result_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_result_char,
         target = DX_malaria_char)

malaria_diagnosis_links2 <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 0) %>% 
  select(TEST_malaria_done_char, DX_malaria_char) %>%
  count(TEST_malaria_done_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_done_char,
         target = DX_malaria_char)

antimalarials_links <- facility1_df %>%
  select(DX_malaria_char, RX_antimalarials_char) %>%
  count(DX_malaria_char, RX_antimalarials_char) %>%
  rename(source = DX_malaria_char,
         target = RX_antimalarials_char)

# combine links
links <- bind_rows(link_CLIN_fever_and_MEAS_temperature,
                   fever_measured_links,
                   malaria_test_links,
                   malaria_test_links2,
                   malaria_results_links,
                   malaria_diagnosis_links,
                   malaria_diagnosis_links2,
                   antimalarials_links)

# The unique node names
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
  )

# match to numbers, not names
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

p <- sankeyNetwork(
  Links = links,
  Nodes = nodes,
  Source = "IDsource",
  Target = "IDtarget",
  Value = "n",
  NodeID = "name",
  units = "children",
  fontSize = 12,
  nodeWidth = 30,
  iterations = 0,
  sinksRight = FALSE)        # ensure node order is as in data
p
```
:::

## Malaria tests

-   malaria tests of those with history or measured fever

```{r}
table(df$CALC_fever_all, df$TEST_malaria_result)
```

```{r}
df %>%
  dplyr::filter(CALC_fever_all == 1) %>%
  dplyr::select(TEST_malaria_result,
                CTX_facility_ID) %>%
  gtsummary::tbl_summary(by = CTX_facility_ID)
```

## Malaria treatments

-   malaria diagnoses vs. positive tests vs. treatments

```{r}
df <- df %>%
  dplyr::mutate(TEST_malaria_positive = 1* (TEST_malaria_result == 1))
table(df$TEST_malaria_result, df$DX_malaria, df$RX_antimalarials) %>% 
  knitr::kable()
```

```{r}
df %>%
  dplyr::filter(TEST_malaria_positive == 1) %>%
  dplyr::select(DX_malaria,
                RX_antimalarials,
                CTX_facility_ID) %>%
  gtsummary::tbl_summary(by = CTX_facility_ID)
```

```{r}
UpSetR::upset(df %>%
                dplyr::select(RX_ACT, RX_AL, RX_artemether, RX_artesunate, RX_primaquine, RX_quinine) %>% 
                dplyr::mutate(across(c(RX_ACT, RX_AL, RX_artemether, RX_artesunate, RX_primaquine, RX_quinine), as.integer)),
  sets = c("RX_ACT", "RX_AL", "RX_artemether", "RX_artesunate", "RX_primaquine", "RX_quinine"),
  order.by = "freq",
  sets.bar.color = c("blue", "red", "yellow", "darkgreen", "orange", "green"), # optional colors
  empty.intersections = "on",
  # nsets = 3,
  number.angles = 0,
  point.size = 3.5,
  line.size = 2, 
  mainbar.y.label = "Antimalarial prescriptions",
  sets.x.label = "Children with antimalarials")
```

