---
title: ":orange_book: Malaria case study - Report"
execute:
  echo: false
  warning: false
from: markdown+emoji
toc: true
number-sections: true
---

## Introduction

``` {{r}}
install.packages("ggplot2")
install.packages("ggthemes")
install.packages("networkD3")
install.packages("apyramid")
```

```{r}
library(openxlsx)
library(dplyr)
library(skimr)
library(gtsummary)
library(finalfit)
library(ggplot2)
library(ggthemes)
library(networkD3) # For alluvial/Sankey diagrams
library(tidyverse)
```
### Import the data

Data are stored in **dataset1.dta**.

#### :pencil2: Exercise 1 {.unnumbered}

1.  Import the dataset and store it into a dataframe called **df**.
2.  Select columns **child_ID**, **CTX_month**, **CTX_district**, **SDC_age_in_months** for the first **5** rows in data frame `df`.
3.  Display in a table with the following characteristics:
    a.  Align the content of the first column to the left and the content of the other 3 columns to the centre.
    b.  Add a caption.

```{r}
#| df-print: kable

# 1. Import the dataset and store it into a dataframe called **df**. 
df <- openxlsx::read.xlsx("./data/dataset1.xlsx")

df %>%
  # 2. Select columns **child_ID**, **CTX_month**, **CTX_district**, **SDC_age_in_months** for the first **5** rows in data frame `df`.
  head(5) %>%
  dplyr::select(child_ID,
                CTX_month,
                CTX_district,
                SDC_age_in_months) %>%
  # 3. Display in a table
  knitr::kable(align = c('l', 'c', 'c', 'c'),
               caption = "Extract of the database")
```

## Population characteristics

### Codebook

+-----------------------------+---------------+
| Variable                    | Coding        |
+=============================+===============+
| SDC_age_in_months            |               |
+-----------------------------+---------------+
| SDC_sex                     | 1: male\      |
|                             | 2: female\    |
|                             | 98: unknown   |
+-----------------------------+---------------+
| CLIN_fever                  | 0: no\        |
|                             | 1: yes\       |
|                             | 98: not sure  |
+-----------------------------+---------------+
| CLIN_fever_onset            |               |
+-----------------------------+---------------+
| CLIN_cough                  | 0: no\        |
|                             | 1: yes\       |
|                             | 98: not sure  |
+-----------------------------+---------------+
| CLIN_diarrhoea              | 0: no\        |
|                             | 1: yes\       |
|                             | 98: not sure  |
+-----------------------------+---------------+
| RX_preconsult_antibiotics   |               |
+-----------------------------+---------------+
| RX_preconsult_antimalarials |               |
+-----------------------------+---------------+
| CTX_district            | Kaliua\       |
|                             | Sengerema\    |
|                             | Tanga         |
+-----------------------------+---------------+
| CTX_area                | urban\        |
|                             | rural         |
+-----------------------------+---------------+
| CTX_facility_type       | dispensary\   |
|                             | health centre |
+-----------------------------+---------------+

```{r}
df$SDC_sex = as.factor(df$SDC_sex)
df$CLIN_fever = as.factor(df$CLIN_fever)
df$CLIN_cough = as.factor(df$CLIN_cough)
df$CLIN_diarrhoea = as.factor(df$CLIN_diarrhoea)
df$RX_preconsult_antibiotics = as.factor(df$RX_preconsult_antibiotics)
df$RX_preconsult_antimalarials = as.factor(df$RX_preconsult_antimalarials)
df$CTX_district = as.factor(df$CTX_district)
df$CTX_area = as.factor(df$CTX_area)
df$CTX_facility_type = as.factor(df$CTX_facility_type)
```

### Structure of the data

#### :pencil2: Exercise 2 {.unnumbered}

Add the following two new variables to data frame `df`

+---------------------------+---------------+
| Variable                  | Coding        |
+===========================+===============+
| SDC_age_category          | \<2 months\   |
|                           | 2-11 months\  |
|                           | 12-23 months\ |
|                           | 24-35 months\ |
|                           | 36-47 months\ |
|                           | 48-59 months  |
+---------------------------+---------------+
| CLIN_fever_onset_category | \<2 days\     |
|                           | 2-3 days\     |
|                           | 4-6 days\     |
|                           | ≥ 7 days      |
+---------------------------+---------------+

::: callout-tip
-   Stata: use the gen command
-   R: use the [mutate](https://dplyr.tidyverse.org/reference/mutate.html) and [case_when](https://dplyr.tidyverse.org/reference/case_when.html) functions from the `dplyr` package
:::

```{r}
df <- df %>%
  dplyr::mutate(
    SDC_age_category = dplyr::case_when(
      SDC_age_in_months < 2 ~ "<2 months",
      SDC_age_in_months >= 2 & SDC_age_in_months < 12 ~ "02-11 months",
      SDC_age_in_months >= 12 & SDC_age_in_months < 24 ~ "12-23 months",
      SDC_age_in_months >= 24 & SDC_age_in_months < 36 ~ "24-35 months",
      SDC_age_in_months >= 36 & SDC_age_in_months < 48 ~ "36-47 months",
      SDC_age_in_months >= 48 & SDC_age_in_months < 60 ~ "48-59 months",
      TRUE ~ ""
    )
  ) %>% 
  dplyr::mutate(
    CLIN_fever_onset_category = dplyr::case_when(
      CLIN_fever_onset < 2 ~ "<2 days",
      CLIN_fever_onset >= 2 & CLIN_fever_onset < 4 ~ "2-3 days",
      CLIN_fever_onset >= 4 & CLIN_fever_onset < 7 ~ "4-6 days",
      CLIN_fever_onset >= 7 ~ ">= 7 days",
      TRUE ~ ""
    )
  )
```

```{r}
df$SDC_age_category = as.factor(df$SDC_age_category)
df$CLIN_fever_onset = as.factor(df$CLIN_fever_onset)
```


#### :pencil2: Exercise 3 {.unnumbered}

Examine the structure of the data, including variable names, labels.

::: callout-tip
-   Stata: use the [codebook](https://www.stata.com/manuals/dcodebook.pdf) command
-   R: use the [skim](https://docs.ropensci.org/skimr/reference/skim.html) function from the `skimr` package
:::

```{r}
df %>%
  skim(SDC_age_in_months,
       SDC_sex,
       CLIN_fever,
       CLIN_fever_onset,
       CLIN_diarrhoea,
       CLIN_cough,
       RX_preconsult_antibiotics,
       RX_preconsult_antimalarials,
       CTX_district,
       CTX_area,
       CTX_facility_type)
```

#### :pencil2: Exercise 4 {.unnumbered}

Display descriptive statistics for the population characteristics.

::: callout-tip
-   Stata
-   R: use the [tbl_summary](https://www.danieldsjoberg.com/gtsummary/reference/tbl_summary.html) function from the `gtsummary` package
:::

```{r}
df %>%
  dplyr::select(SDC_age_category,
                SDC_sex,
                CLIN_fever,
                CLIN_fever_onset_category,
                CLIN_diarrhoea,
                CLIN_cough,
                RX_preconsult_antibiotics,
                RX_preconsult_antimalarials,
                CTX_district,
                CTX_area,
                CTX_facility_type) %>%
  gtsummary::tbl_summary(missing_text = "(Missing)")
```
### Age pyramid

```{r}
apyramid::age_pyramid(data = df,
                      age_group = "SDC_age_category",
                      split_by = "SDC_sex",
                      na.rm = TRUE)
```

```{r}
apyramid::age_pyramid(data = df,
                      age_group = "SDC_age_category",
                      split_by = "CLIN_fever",
                      na.rm = TRUE)
```
```{r}
apyramid::age_pyramid(data = df,
                      age_group = "SDC_age_category",
                      split_by = "CLIN_cough",
                      na.rm = TRUE)
```
```{r}
apyramid::age_pyramid(data = df,
                      age_group = "SDC_age_category",
                      split_by = "CLIN_diarrhoea",
                      na.rm = TRUE)
```

## Healthcare provider actions

### Codebook

-   Temperature measured
    -   Fever measured
-   Fever (temp or history)
-   Malaria test
-   Any severe diagnosis
-   Malaria diagnosis
-   Malaria treatment
-   Referral

+-----------------------------+------------------------+
| Variable                    | Coding                 |
+=============================+========================+
| MEAS_temperature            |                        |
+-----------------------------+------------------------+
|                             |                        |
+-----------------------------+------------------------+
| TEST_malaria_result         | 0: negative\           |
|                             | 1: positive\           |
|                             | 2: indeterminate\      |
|                             | 95: unreadable result\ |
|                             | 98: not sure           |
+-----------------------------+------------------------+
| DX_malaria                  | 0: no\                 |
|                             | 1: yes                 |
+-----------------------------+------------------------+
| RX_antimalarials            | 0: no\                 |
|                             | 1: yes                 |
+-----------------------------+------------------------+
| MGMT_referral_src_caregiver |                        |
+-----------------------------+------------------------+
| MGMT_referral_src_registry  |                        |
+-----------------------------+------------------------+

### Structure of the data

#### :pencil2: Exercise 5

Examine the structure of the data, including variable names, labels.

::: callout-tip
-   Stata: use the [codebook](https://www.stata.com/manuals/dcodebook.pdf) command
-   R: use the [skim](https://docs.ropensci.org/skimr/reference/skim.html) function from the `skimr` package
:::

#### R

```{r}

df$TEST_malaria_done = as.factor(df$TEST_malaria_done)

df %>%
  skimr::skim(MEAS_temperature,
              TEST_malaria_done,
              TEST_malaria_result,
              DX_malaria,
              RX_antimalarials,
              MGMT_referral_src_caregiver,
              MGMT_referral_src_registry)
```

#### :pencil2: Exercise 3

Add the following two new variables to data frame `df`

-   MEAS_fever
-   Fever (temp or history)

::: callout-tip
-   Stata: use the gen command
-   R: use the mutate function from the `dplyr` package
:::

```{r}
df <- df %>%
  dplyr::mutate(CALC_temperature_measured = 1 * (!is.na(MEAS_temperature))) %>%
  dplyr::mutate(CALC_fever = 1 * (MEAS_temperature >= 37.5)) %>%
  dplyr::mutate(CALC_fever_or_temp = (CLIN_fever == 1) | (CALC_fever == 1))
```

#### :pencil2: Exercise 6

Display descriptive statistics for the following healthcare provider actions:

::: callout-tip
-   R: use the [tbl_summary](https://www.danieldsjoberg.com/gtsummary/reference/tbl_summary.html) function from the `gtsummary` package
:::

```{r}
df %>%
  dplyr::select(CALC_temperature_measured,
                CALC_fever,
                CALC_fever_or_temp,
                TEST_malaria_done,
                TEST_malaria_result,
                DX_malaria,
                RX_antimalarials,
                MGMT_referral_src_caregiver,
                MGMT_referral_src_registry) %>%
  gtsummary::tbl_summary(missing_text = "(Missing)")
```

## Number of consultations by facility

### :pencil2: Exercise 6

Plot the number of consultations by facility in bars, grouped by district.

::: callout-tip
-   Stata:
-   R:
:::

```{r}
df %>%
  dplyr::group_by(CTX_district,
                  CTX_facility_ID) %>%
  count() %>% 
  ggplot2::ggplot(aes(x = haven::as_factor(CTX_district),
                      y = n)) + 
  ggplot2::geom_bar(position = position_dodge2(preserve = "single"),
                    stat="identity") +
  ggplot2::labs(x = "", y = "No. consultations") +
  ggthemes::theme_hc()
```

## Fever assessment

```{r}
df <- df %>%
  dplyr::mutate(CALC_temperature_measured_char = ifelse(!is.na(MEAS_temperature), "Temperature recorded", "Temperature not recorded")) %>%
  dplyr::mutate(CALC_fever_char = ifelse(MEAS_temperature >= 37.5, "Temperature >= 37.5°C", "Temperature < 37.5°C")) %>%
  dplyr::mutate(CLIN_fever_char = ifelse(CLIN_fever == 1, "History of fever", "No history of fever")) %>% 
  dplyr::mutate(TEST_malaria_done_char = ifelse(TEST_malaria_done == 1, "Malaria test recorded", "Malaria test not recorded")) %>% 
  dplyr::mutate(
    TEST_malaria_result_char = dplyr::case_when(
      TEST_malaria_result == 0 ~ "Malaria result negative",
      TEST_malaria_result == 1 ~ "Malaria result positive",
      TEST_malaria_result == 2 ~ "Malaria result indeterminate",
      TEST_malaria_result == 95 ~ "Malaria result unreadable",
      TEST_malaria_result == 98 ~ "Malaria result unknown",
      TRUE ~ ""
    )
  ) %>%
  dplyr::mutate(DX_malaria_char = ifelse(DX_malaria == 1, "Malaria diagnosis", "No malaria diagnosis")) %>% 
  dplyr::mutate(RX_antimalarials_char = ifelse(RX_antimalarials == 1, "Malaria treatment", "No malaria treatment"))
```

:::{.column-page}

```{r}
link_CLIN_fever_and_MEAS_temperature <- df %>%
  select(CLIN_fever_char, CALC_temperature_measured_char) %>%
  count(CLIN_fever_char, CALC_temperature_measured_char) %>%
  rename(source = CLIN_fever_char,
         target = CALC_temperature_measured_char)

fever_measured_links <- df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>% 
  select(CALC_temperature_measured_char, CALC_fever_char) %>%
  count(CALC_temperature_measured_char, CALC_fever_char) %>% 
  rename(source = CALC_temperature_measured_char,
         target = CALC_fever_char)

malaria_test_links <- df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>%
  select(CALC_fever_char, TEST_malaria_done_char) %>%
  count(CALC_fever_char, TEST_malaria_done_char) %>%
  rename(source = CALC_fever_char,
         target = TEST_malaria_done_char)

malaria_test_links2 <- df %>%
  dplyr::filter(CALC_temperature_measured == 0) %>%
  select(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  count(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  rename(source = CALC_temperature_measured_char,
         target = TEST_malaria_done_char)

malaria_results_links <- df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  count(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  rename(source = TEST_malaria_done_char,
         target = TEST_malaria_result_char)

malaria_diagnosis_links <- df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_result_char, DX_malaria_char) %>%
  count(TEST_malaria_result_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_result_char,
         target = DX_malaria_char)

malaria_diagnosis_links2 <- df %>%
  dplyr::filter(TEST_malaria_done == 0) %>% 
  select(TEST_malaria_done_char, DX_malaria_char) %>%
  count(TEST_malaria_done_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_done_char,
         target = DX_malaria_char)

antimalarials_links <- df %>%
  select(DX_malaria_char, RX_antimalarials_char) %>%
  count(DX_malaria_char, RX_antimalarials_char) %>%
  rename(source = DX_malaria_char,
         target = RX_antimalarials_char)

# combine links
links <- bind_rows(link_CLIN_fever_and_MEAS_temperature,
                   fever_measured_links,
                   malaria_test_links,
                   malaria_test_links2,
                   malaria_results_links,
                   malaria_diagnosis_links,
                   malaria_diagnosis_links2,
                   antimalarials_links)

# The unique node names
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
  )

# match to numbers, not names
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

p <- sankeyNetwork(
  Links = links,
  Nodes = nodes,
  Source = "IDsource",
  Target = "IDtarget",
  Value = "n",
  NodeID = "name",
  units = "children",
  fontSize = 12,
  nodeWidth = 30,
  iterations = 0,
  sinksRight = FALSE)        # ensure node order is as in data
p

#links$group <- as.factor(c("type_a","type_a","type_a","type_b","type_b","type_b"))
 
# Add a 'group' column to each node. Here I decide to put all of them in the same group to make them grey
#nodes$group <- as.factor(c("my_unique_group"))
 
# Give a color for each group:
#my_color <- 'd3.scaleOrdinal() .domain(["type_a", "type_b", "my_unique_group"]) .range(["#69b3a2", "steelblue", "grey"])'
```

:::

### Facility F9514

:::{.column-page}

```{r}
facility1_df <- df %>%
  dplyr::filter(CTX_facility_ID == "F9514")

link_CLIN_fever_and_MEAS_temperature <- facility1_df %>%
  select(CLIN_fever_char, CALC_temperature_measured_char) %>%
  count(CLIN_fever_char, CALC_temperature_measured_char) %>%
  rename(source = CLIN_fever_char,
         target = CALC_temperature_measured_char)

fever_measured_links <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>% 
  select(CALC_temperature_measured_char, CALC_fever_char) %>%
  count(CALC_temperature_measured_char, CALC_fever_char) %>% 
  rename(source = CALC_temperature_measured_char,
         target = CALC_fever_char)

malaria_test_links <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>%
  select(CALC_fever_char, TEST_malaria_done_char) %>%
  count(CALC_fever_char, TEST_malaria_done_char) %>%
  rename(source = CALC_fever_char,
         target = TEST_malaria_done_char)

malaria_test_links2 <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 0) %>%
  select(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  count(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  rename(source = CALC_temperature_measured_char,
         target = TEST_malaria_done_char)

malaria_results_links <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  count(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  rename(source = TEST_malaria_done_char,
         target = TEST_malaria_result_char)

malaria_diagnosis_links <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_result_char, DX_malaria_char) %>%
  count(TEST_malaria_result_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_result_char,
         target = DX_malaria_char)

malaria_diagnosis_links2 <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 0) %>% 
  select(TEST_malaria_done_char, DX_malaria_char) %>%
  count(TEST_malaria_done_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_done_char,
         target = DX_malaria_char)

antimalarials_links <- facility1_df %>%
  select(DX_malaria_char, RX_antimalarials_char) %>%
  count(DX_malaria_char, RX_antimalarials_char) %>%
  rename(source = DX_malaria_char,
         target = RX_antimalarials_char)

# combine links
links <- bind_rows(link_CLIN_fever_and_MEAS_temperature,
                   fever_measured_links,
                   malaria_test_links,
                   malaria_test_links2,
                   malaria_results_links,
                   malaria_diagnosis_links,
                   malaria_diagnosis_links2,
                   antimalarials_links)

# The unique node names
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
  )

# match to numbers, not names
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

p <- sankeyNetwork(
  Links = links,
  Nodes = nodes,
  Source = "IDsource",
  Target = "IDtarget",
  Value = "n",
  NodeID = "name",
  units = "children",
  fontSize = 12,
  nodeWidth = 30,
  iterations = 0,
  sinksRight = FALSE)        # ensure node order is as in data
p
```
:::

### Facility F7476

:::{.column-page}

```{r}
facility1_df <- df %>% dplyr::filter(CTX_facility_ID == "F7476")

link_CLIN_fever_and_MEAS_temperature <- facility1_df %>%
  select(CLIN_fever_char, CALC_temperature_measured_char) %>%
  count(CLIN_fever_char, CALC_temperature_measured_char) %>%
  rename(source = CLIN_fever_char,
         target = CALC_temperature_measured_char)

fever_measured_links <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>% 
  select(CALC_temperature_measured_char, CALC_fever_char) %>%
  count(CALC_temperature_measured_char, CALC_fever_char) %>% 
  rename(source = CALC_temperature_measured_char,
         target = CALC_fever_char)

malaria_test_links <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 1) %>%
  select(CALC_fever_char, TEST_malaria_done_char) %>%
  count(CALC_fever_char, TEST_malaria_done_char) %>%
  rename(source = CALC_fever_char,
         target = TEST_malaria_done_char)

malaria_test_links2 <- facility1_df %>%
  dplyr::filter(CALC_temperature_measured == 0) %>%
  select(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  count(CALC_temperature_measured_char, TEST_malaria_done_char) %>%
  rename(source = CALC_temperature_measured_char,
         target = TEST_malaria_done_char)

malaria_results_links <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  count(TEST_malaria_done_char, TEST_malaria_result_char) %>%
  rename(source = TEST_malaria_done_char,
         target = TEST_malaria_result_char)

malaria_diagnosis_links <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 1) %>% 
  select(TEST_malaria_result_char, DX_malaria_char) %>%
  count(TEST_malaria_result_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_result_char,
         target = DX_malaria_char)

malaria_diagnosis_links2 <- facility1_df %>%
  dplyr::filter(TEST_malaria_done == 0) %>% 
  select(TEST_malaria_done_char, DX_malaria_char) %>%
  count(TEST_malaria_done_char, DX_malaria_char) %>%
  rename(source = TEST_malaria_done_char,
         target = DX_malaria_char)

antimalarials_links <- facility1_df %>%
  select(DX_malaria_char, RX_antimalarials_char) %>%
  count(DX_malaria_char, RX_antimalarials_char) %>%
  rename(source = DX_malaria_char,
         target = RX_antimalarials_char)

# combine links
links <- bind_rows(link_CLIN_fever_and_MEAS_temperature,
                   fever_measured_links,
                   malaria_test_links,
                   malaria_test_links2,
                   malaria_results_links,
                   malaria_diagnosis_links,
                   malaria_diagnosis_links2,
                   antimalarials_links)

# The unique node names
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
  )

# match to numbers, not names
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

p <- sankeyNetwork(
  Links = links,
  Nodes = nodes,
  Source = "IDsource",
  Target = "IDtarget",
  Value = "n",
  NodeID = "name",
  units = "children",
  fontSize = 12,
  nodeWidth = 30,
  iterations = 0,
  sinksRight = FALSE)        # ensure node order is as in data
p
```

:::

Sequence

-   temp measurement by reported fever; by facility

```{r}

df$CTX_facility_ID <- haven::as_factor(df$CTX_facility_ID) 
df %>%
  dplyr::select(MEAS_temperature,
                CTX_facility_ID) %>%
  gtsummary::tbl_summary(by = CTX_facility_ID) %>%
  add_p()
```

-   also showing 'prevalence' of fever when of whole clinic vs of those who measure to indicate bias

## Malaria tests

-   malaria tests of those with history or measured fever

```{r}
table(df$CALC_fever_or_temp, df$TEST_malaria_result)
```

```{r}
df$CTX_facility_ID <- haven::as_factor(df$CTX_facility_ID) 
df %>%
  dplyr::filter(CALC_fever_or_temp == 1) %>%
  dplyr::select(TEST_malaria_result,
                CTX_facility_ID) %>%
  gtsummary::tbl_summary(by = CTX_facility_ID)
```

## Malaria treatments

-   malaria diagnoses vs. positive tests vs. treatment.

```{r}
df <- df %>%
  dplyr::mutate(TEST_malaria_positive = 1* (TEST_malaria_result == 1))
table(df$TEST_malaria_result, df$DX_malaria, df$RX_antimalarials) %>% knitr::kable()
```

```{r}
df$CTX_facility_ID <- haven::as_factor(df$CTX_facility_ID) 
df %>%
  dplyr::filter(TEST_malaria_positive == 1) %>%
  dplyr::select(DX_malaria,
                RX_antimalarials,
                CTX_facility_ID) %>%
  gtsummary::tbl_summary(by = CTX_facility_ID)
```
