---
title: ":orange_book: Malaria case study - Part 2"
warning: false
---

## Introduction

### Overview

These pages will demonstrate use of Quarto with data from Tanzania.

### Learning objectives

## Malaria research questions

Research questions in an enumerated list

## Getting started

#### Access the datasets

Download the dataset (Excel) here

#### Access the version of the Quarto template

Download the final Quarto template used in this case study, to follow-along step-by-step uisng GitHub

#### Quarto resources

Review the R Basics page "Reading a RMarkdown Script", or reference these resources: Rmarkdown introduction and Rmarkdown authoring basics.

```{{r}}
install.packages("ggplot2")
install.packages("ggthemes")
```

### Dataset description

Dataset 1 + SPA data

### Data collection

### Import the data

::: panel-tabset

#### :pencil2: Exercise 1

Read the dataset and store it into a dataframe called **df**.

::: callout-tip
Refer to @sec-import-data-from-files
:::

```{r}
#| echo: fenced
# Write your code here
```

#### R

```{r}
#| echo: fenced
library(haven)
df <- haven::read_dta("./data/dataset2.dta")
```

:::