---
title: ":orange_book: Malaria case study - Comparison of RCT and SPA entries"
execute:
  echo: false
  warning: false
from: markdown+emoji
toc: true
number-sections: true
---

## Introduction

Sensitivity analysis definition

how SPA observations affect RCT consultations and data recording

``` {{r}}
install.packages("ggplot2")
install.packages("ggthemes")
install.packages("networkD3")
install.packages("apyramid")
```

```{r}
library(openxlsx)
library(dplyr)
library(skimr)
library(gtsummary)
library(finalfit)
library(ggplot2)
library(ggthemes)
library(networkD3) # For alluvial/Sankey diagrams
library(tidyverse)
```

### Import the data

Data are stored in **dataset2.dta**.

#### :pencil2: Exercise 1 {.unnumbered}

1.  Import the dataset and store it into a dataframe called **df**.
2.  Select columns **RCT_child_ID**, **RCT_CLIN_fever**, **SPA_CLIN_fever_reported**, **SPA_CLIN_fever_investigated** for the first **10** rows in data frame `df`.
3.  Display in a table with the following characteristics:
    a.  Align the content of the first column to the left and the content of the other 3 columns to the centre.
    b.  Add a caption.

```{r}
#| df-print: kable

# 1. Import the dataset and store it into a dataframe called **df**. 
df <- openxlsx::read.xlsx("./data/dataset2.xlsx")

df %>%
  # 2. Select columns **child_ID**, **CTX_month**, **CTX_district**, **SDC_age_in_months** for the first **10** rows in data frame `df`.
  head(10) %>%
  dplyr::select(RCT_child_ID,
                RCT_CLIN_fever,
                SPA_CLIN_fever_reported,
                SPA_CLIN_fever_investigated) %>%
  # 3. Display in a table
  knitr::kable(align = c('l', 'c', 'c', 'c'),
               caption = "Extract of the database")
```
### Clinical presentation

```{r}
df <- df %>%
  dplyr::mutate(SPA_CLIN_fever_reported_char = ifelse(SPA_CLIN_fever_reported == 1, "Fever complaint (SPA)", "No fever complaint (SPA)")) %>%
  dplyr::mutate(SPA_CLIN_fever_investigated_char = ifelse(SPA_CLIN_fever_investigated == 1, "Fever asked (SPA)", "Fever not asked (SPA)")) %>%
  dplyr::mutate(SPA_CLIN_fever_char = ifelse(SPA_CLIN_fever == 1, "Fever (SPA)", "No fever (SPA)")) %>%
  dplyr::mutate(
    RCT_CLIN_fever_char = dplyr::case_when(
      RCT_CLIN_fever == 1 ~ "Fever (RCT)",
      RCT_CLIN_fever == 0 ~ "No fever (RCT)",
      RCT_CLIN_fever == 98 ~ "Unknown (RCT)",
      TRUE ~ ""
    )
  ) %>%
  dplyr::mutate(SPA_CLIN_fever_tot_char = ifelse(SPA_CLIN_fever_reported == 1, "Fever (SPA)", SPA_CLIN_fever_char)) %>% 
  dplyr::mutate(
    SPA_CLIN_fever_tot_char = dplyr::case_when(
      SPA_CLIN_fever_reported == 1 ~ "Fever (SPA)",
      SPA_CLIN_fever_investigated == 1 ~ SPA_CLIN_fever_char,
      SPA_CLIN_fever_investigated == 0 ~ "Unknown (SPA)",
      TRUE ~ ""
    )
  )
```

```{r}
#| df-print: kable
table(df$RCT_CLIN_fever_char, df$SPA_CLIN_fever_reported_char) %>%
  knitr::kable()
```
```{r}
#| df-print: kable
table(df$RCT_CLIN_fever_char, df$SPA_CLIN_fever_tot_char) %>%
  knitr::kable()
```
```{r}
long_prop <- data.frame(prop.table(table(rct = df$RCT_CLIN_fever_char, spa= df$SPA_CLIN_fever_tot_char)))
ggplot2::ggplot(data = long_prop)+       # use long data, with proportions as Freq
  ggplot2::geom_tile(                    # visualize it in tiles
    aes(
      x = spa,         # x-axis is case age
      y = rct,     # y-axis is infector age
      fill = Freq))+            # color of the tile is the Freq column in the data
  scale_fill_gradient(          # adjust the fill color of the tiles
    low = "white",
    high = "dark green")+
  labs(                         # labels
    x = "SPA",
    y = "RCT",
    title = "Fever",
    subtitle = "Frequency matrix",
    fill = "Proportion of children"     # legend title
  )
```

::: column-page

```{r}
link1 <- df %>%
  dplyr::filter(SPA_CLIN_fever_reported == 0) %>%
  select(SPA_CLIN_fever_reported_char, SPA_CLIN_fever_investigated_char) %>%
  count(SPA_CLIN_fever_reported_char, SPA_CLIN_fever_investigated_char) %>%
  rename(source = SPA_CLIN_fever_reported_char,
         target = SPA_CLIN_fever_investigated_char)

link2 <- df %>%
  dplyr::filter(SPA_CLIN_fever_investigated == 1) %>% 
  select(SPA_CLIN_fever_investigated_char, SPA_CLIN_fever_char) %>%
  count(SPA_CLIN_fever_investigated_char, SPA_CLIN_fever_char) %>% 
  rename(source = SPA_CLIN_fever_investigated_char,
         target = SPA_CLIN_fever_char)

link3 <- df %>%
  dplyr::filter(SPA_CLIN_fever_reported == 1) %>% 
  select(SPA_CLIN_fever_reported_char, RCT_CLIN_fever_char) %>%
  count(SPA_CLIN_fever_reported_char, RCT_CLIN_fever_char) %>% 
  rename(source = SPA_CLIN_fever_reported_char,
         target = RCT_CLIN_fever_char)

link4 <- df %>%
  dplyr::filter(SPA_CLIN_fever_investigated == 0) %>%
  select(SPA_CLIN_fever_investigated_char, RCT_CLIN_fever_char) %>%
  count(SPA_CLIN_fever_investigated_char, RCT_CLIN_fever_char) %>% 
  rename(source = SPA_CLIN_fever_investigated_char,
         target = RCT_CLIN_fever_char)

link5 <- df %>%
  dplyr::filter(SPA_CLIN_fever_investigated == 1) %>%
  select(SPA_CLIN_fever_char, RCT_CLIN_fever_char) %>%
  count(SPA_CLIN_fever_char, RCT_CLIN_fever_char) %>% 
  rename(source = SPA_CLIN_fever_char,
         target = RCT_CLIN_fever_char)

# combine links
links <- bind_rows(link1,
                   link2,
                   link3,
                   link4,
                   link5)

# The unique node names
nodes <- data.frame(
  name=c(as.character(links$source), as.character(links$target)) %>% 
    unique()
  )

# match to numbers, not names
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1

p <- sankeyNetwork(
  Links = links,
  Nodes = nodes,
  Source = "IDsource",
  Target = "IDtarget",
  Value = "n",
  NodeID = "name",
  units = "children",
  fontSize = 12,
  nodeWidth = 30,
  iterations = 0,
  sinksRight = FALSE)        # ensure node order is as in data
p
```
:::

### Temperature measurement

### Malaria tests