---
title: ":orange_book: Malaria case study - RCT sensitivity analysis"
execute:
  echo: false
  warning: false
from: markdown+emoji
toc: true
number-sections: true
---

## Introduction

Sensitivity analysis definition

how SPA observations affect RCT consultations and data recording

``` {{r}}
install.packages("ggplot2")
install.packages("ggthemes")
install.packages("networkD3")
install.packages("apyramid")
```

```{r}
library(openxlsx)
library(dplyr)
library(skimr)
library(gtsummary)
library(finalfit)
library(ggplot2)
library(ggthemes)
library(networkD3) # For alluvial/Sankey diagrams
library(tidyverse)
```

### Import the data

Data are stored in **dataset1.dta**.

#### :pencil2: Exercise 1 {.unnumbered}

1.  Import the dataset and store it into a dataframe called **df**.
2.  Select columns **child_ID**, **CTX_month**, **CTX_district**, **SDC_age_in_months** for the first **5** rows in data frame `df`.
3.  Display in a table with the following characteristics:
    a.  Align the content of the first column to the left and the content of the other 3 columns to the centre.
    b.  Add a caption.

```{r}
#| df-print: kable

# 1. Import the dataset and store it into a dataframe called **df**. 
df <- openxlsx::read.xlsx("./data/dataset1.xlsx")

df %>%
  # 2. Select columns **child_ID**, **CTX_month**, **CTX_district**, **SDC_age_in_months** for the first **5** rows in data frame `df`.
  head(5) %>%
  dplyr::select(child_ID,
                CTX_month,
                CTX_district,
                SDC_age_in_months) %>%
  # 3. Display in a table
  knitr::kable(align = c('l', 'c', 'c', 'c'),
               caption = "Extract of the database")
```

## Population characteristics

### Codebook

+-----------------------------+---------------+
| Variable                    | Coding        |
+=============================+===============+
| SDC_age_in_months           | |             |
+-----------------------------+---------------+
| SDC_sex                     | 1: male       |
|                             |               |
|                             | 2: female     |
|                             |               |
|                             | 98: unknown   |
+-----------------------------+---------------+
| CLIN_fever                  | 0: no         |
|                             |               |
|                             | 1: yes        |
|                             |               |
|                             | 98: not sure  |
+-----------------------------+---------------+
| CLIN_fever_onset            |               |
+-----------------------------+---------------+
| CLIN_cough                  | 0: no         |
|                             |               |
|                             | 1: yes        |
|                             |               |
|                             | 98: not sure  |
+-----------------------------+---------------+
| CLIN_diarrhoea              | 0: no         |
|                             |               |
|                             | 1: yes        |
|                             |               |
|                             | 98: not sure  |
+-----------------------------+---------------+
| RX_preconsult_antibiotics   | 0: no         |
|                             |               |
|                             | 1: yes        |
+-----------------------------+---------------+
| RX_preconsult_antimalarials | 0: no         |
|                             |               |
|                             | 1: yes        |
+-----------------------------+---------------+
| CTX_district                | Kaliua        |
|                             |               |
|                             | Sengerema     |
|                             |               |
|                             | Tanga         |
+-----------------------------+---------------+
| CTX_area                    | urban         |
|                             |               |
|                             | rural         |
+-----------------------------+---------------+
| CTX_facility_type           | dispensary    |
|                             |               |
|                             | health centre |
+-----------------------------+---------------+

```{r}
df$SDC_sex = as.factor(df$SDC_sex)
df$CLIN_fever = as.factor(df$CLIN_fever)
df$CLIN_cough = as.factor(df$CLIN_cough)
df$CLIN_diarrhoea = as.factor(df$CLIN_diarrhoea)
df$RX_preconsult_antibiotics = as.factor(df$RX_preconsult_antibiotics)
df$RX_preconsult_antimalarials = as.factor(df$RX_preconsult_antimalarials)
df$CTX_district = as.factor(df$CTX_district)
df$CTX_area = as.factor(df$CTX_area)
df$CTX_facility_type = as.factor(df$CTX_facility_type)
df$CTX_SPA_obs = as.factor(df$CTX_SPA_obs)
df$CTX_SPA_obs_after_lab = as.factor(df$CTX_SPA_obs_after_lab)
```

```{r}
df <- df %>%
  dplyr::mutate(CALC_temperature_measured = 1 * (!is.na(MEAS_temperature))) %>%
  dplyr::mutate(CALC_fever = 1 * (MEAS_temperature >= 37.5)) %>%
  dplyr::mutate(CALC_fever_or_temp = (CLIN_fever == 1) | (CALC_fever == 1))
```

### Structure of the data

#### :pencil2: Exercise 2 {.unnumbered}

Add the following two new variables to data frame `df`

+---------------------------+---------------+
| Variable                  | Coding        |
+===========================+===============+
| SDC_age_category          | \<2 months    |
|                           |               |
|                           | 2-11 months   |
|                           |               |
|                           | 12-23 months  |
|                           |               |
|                           | 24-35 months  |
|                           |               |
|                           | 36-47 months  |
|                           |               |
|                           | 48-59 months  |
+---------------------------+---------------+
| CLIN_fever_onset_category | \<2 days      |
|                           |               |
|                           | 2-3 days      |
|                           |               |
|                           | 4-6 days      |
|                           |               |
|                           | ≥ 7 days      |
+---------------------------+---------------+

::: callout-tip
-   Stata: use the gen command
-   R: use the [mutate](https://dplyr.tidyverse.org/reference/mutate.html) and [case_when](https://dplyr.tidyverse.org/reference/case_when.html) functions from the `dplyr` package
:::

```{r}
df <- df %>%
  dplyr::mutate(
    SDC_age_category = dplyr::case_when(
      SDC_age_in_months < 2 ~ "<2 months",
      SDC_age_in_months >= 2 & SDC_age_in_months < 12 ~ "02-11 months",
      SDC_age_in_months >= 12 & SDC_age_in_months < 24 ~ "12-23 months",
      SDC_age_in_months >= 24 & SDC_age_in_months < 36 ~ "24-35 months",
      SDC_age_in_months >= 36 & SDC_age_in_months < 48 ~ "36-47 months",
      SDC_age_in_months >= 48 & SDC_age_in_months < 60 ~ "48-59 months",
      TRUE ~ ""
    )
  ) %>% 
  dplyr::mutate(
    CLIN_fever_onset_category = dplyr::case_when(
      CLIN_fever_onset < 2 ~ "<2 days",
      CLIN_fever_onset >= 2 & CLIN_fever_onset < 4 ~ "2-3 days",
      CLIN_fever_onset >= 4 & CLIN_fever_onset < 7 ~ "4-6 days",
      CLIN_fever_onset >= 7 ~ ">= 7 days",
      TRUE ~ ""
    )
  )
```

```{r}
df$SDC_age_category = as.factor(df$SDC_age_category)
df$CLIN_fever_onset = as.factor(df$CLIN_fever_onset)
```

#### :pencil2: Exercise 4 {.unnumbered}

Display descriptive statistics for the population characteristics.

::: callout-tip
-   Stata
-   R: use the [tbl_summary](https://www.danieldsjoberg.com/gtsummary/reference/tbl_summary.html) function from the `gtsummary` package
:::

```{r}
df2 <- data.frame(df)
df2$CTX_SPA_obs <- "All"
df3 <- df %>%
  dplyr::filter(CTX_SPA_obs == 1 | CTX_SPA_obs_after_lab == 1)
df3$CTX_SPA_obs <- "Observed"
df4 <- rbind(df2, df3)
```

```{r}
df4 %>%
  dplyr::select(SDC_age_category,
                SDC_sex,
                CLIN_fever,
                CLIN_fever_onset_category,
                CLIN_diarrhoea,
                CLIN_cough,
                RX_preconsult_antibiotics,
                RX_preconsult_antimalarials,
                CTX_district,
                CTX_area,
                CTX_facility_type,
                CTX_SPA_obs) %>%
  gtsummary::tbl_summary(by = CTX_SPA_obs, missing_text = "(Missing)") %>%
  gtsummary::add_p()
```
```{r}
df4 %>%
  dplyr::select(CALC_temperature_measured,
                CALC_fever,
                CALC_fever_or_temp,
                TEST_malaria_done,
                TEST_malaria_result,
                DX_malaria,
                RX_antimalarials,
                MGMT_referral_src_caregiver,
                MGMT_referral_src_registry,
                CTX_SPA_obs) %>%
  gtsummary::tbl_summary(by = CTX_SPA_obs, missing_text = "(Missing)") %>%
  gtsummary::add_p()
```