---
title: ":blue_book: Manipulate data"
---

## Introduction

::: callout-important
Remember that with Quarto you can:

* store multiple data sets in memory (stored in different data frames `df1`, `df2`, `df3`, etc),
* work in parallel on all these data sets.
:::

## Manipulate Python and R data

::: {.panel-tabset}

#### :pencil2: Exercise 1

1. Import **dataset1.xlsx** using Stata and store it in `df1`

```{r}
#| echo: fenced
# Write your code here
```

2. Import **dataset1.csv** using Python and store it in `df2`

```{python}
#| echo: fenced
# Write your code here
```

3. Compare `df1`and `df2`. Can you indicate what variable has been modified in **dataset1** between df1 and df2?

::: callout-tip
Use the R function **comparedf**
:::

```{r}
#| echo: fenced
# Write your code here
```

#### :eyes: Solution

1. Import **dataset1.xlsx** using Stata and store it in `df1`

```{r}
#| echo: fenced
library(RStata)
df1 <- RStata::stata("import excel ./data/dataset1.xlsx",
                     data.out = TRUE)
```

2. Import **dataset1.csv** using Python and store it in `df2`

```{python}
#| include: false
import warnings
warnings.filterwarnings('ignore')
```

```{python}
#| echo: fenced
import pandas as pd
df2 = pd.read_csv('./data/dataset1.csv')
```

3. Compare `df1`and `df2`.

```{r}
#| echo: fenced
library(reticulate)
arsenal::comparedf(df1, py$df2)
```

:::