---
title: "Code chunks"
---

## Introduction

The number of languages and runtimes used for scientific discourse is very broad (and the RStudio and Jupyter ecosystems in particular are extraordinarily popular).

Quarto was developed to be multilingual, beginning with R, Python, Javascript, and Julia, with the idea that it will work even for languages that don't yet exist.

## Run R code chunks

::: callout-note
A data frame is a two-dimensional array-like structure that contains rows and columns.
:::

To store the content of the *iris* data set in variable `df`, you can use `=` (*equal*) but good practice recommend using `<-` (*back arrow*) to indicate the direction of your allocation.

```{r}
df <- iris
```

How to display data

```{r}
#| echo: fenced
#| df-print: kable
print(df)
```

You can cross-reference your table.

```{r}
#| label: tbl-iris
#| tbl-cap: Iris data set
#| echo: fenced
#| df-print: kable
print(df)
```

## Call Stata commands within R code chunks

`RStata` is a simple R / Stata interface which enable the user to:

* execute Stata commands (both inline and from a .do file) from R;
* pass a data.frame to Stata;
* return a data.frame to R;
* include Stata chunks in knitr documents (however each chunk is independent from the others; feature tested with LaTeX/Linux).

### Configure RStudio to execute Stata

#### Find your Stata binary path

The function `chooseStataBin` from the `RStata` library allows you to browse and set the path to your Stata binary executable.

### Add your Stata binary path to your .Rprofile

The Stata binary path setting we just created will be lost if your RStudio is closed.
To keep this setting each time you are using RStudio, let us add the Stata binary path as an option to `.Rprofile`, which is your user-specific R configuration file.

## Run Python code chunks

For (advanced) Python/R Markdown users only

You still need to import the R package `reticulate` if you want to use the Knitr engine and manipulate Python objects within R code chunks.

```{r}
#| echo: true
library(reticulate)
```

## Manipulation of R objects in Python code chunks

R objects can be manipulated in Python code chunks by referring to them as `r.`

```{r}
#| echo: true
val <- 10
```

```{python}
#| echo: true
val = 5
print(r.val)
```

## Manipulation of Python objects in R code chunks

Python objects can be manipulated in R code chunks by referring to them as `py$`

```{r}
#| echo: true
print(val)
print(py$val)
```

## References
